---
title: "Week 3 HW"
author: "Kamilla G."
date: "2023-02-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
"Learn how to Subset, call specific some what random observations"
source("http://www.openintro.org/stat/data/cdc.R")
```

Show me the 567th row and provide me with the weight 
(6th variable)
```{r}
cat(colnames(cdc))
cat( cdc[567,]$weight )
```

Show me the range 1 to 10 in the 6th variable
```{r}
cat( cdc[1:10, 6] )
```

Subsetting
```{r}

```

Checking subset
#Notes 

How many men do we have in the cdc dataset?
```{r}
cat( dim(subset(cdc, gender=="m"))[1] )
```

What are another 2 ways we can find how many men are in the datasets? 
Using cdc then mdata?
```{r}
cat( dim(cdc[cdc$gender=="m",])[1] )

mdata <- cdc[ which(cdc$gender=="m"), ]
cat( dim(mdata)[1] )
```

I want to know the observation details of men over 30.
```{r}
cat("Men over 30 details")
summary( subset(cdc, gender=="m" & age>30) )
```

I want to know the observation details of men equal to and over 30.
```{r}
cat("Men 30 and over details")
summary( subset(cdc, gender=="m" & age>=30) )
```

What is the mean age of men in this data set?
```{r}
mdata = subset(cdc, gender=="m")
cat(mean(mdata$age))
```

Is this data set positively or negatively skewed?
#Notes

```{r}
amean = mean(mdata$age)
amedian = median(mdata$age)
if(amean>amedian) {
  cat("positively skewed")
} else if(amean<amedian) {
  cat("negaitvely skewed")
} else {
  cat("symmetric")
}
```

Let's look at a comparison of men's current weight vs desired weight
```{r}
plot(mdata$weight, col='blue', pch=19, ylab="weight")
points(mdata$wtdesire, col='green', pch=19)
legend("topleft", 25, pch=c(19, 19), legend=c("actual weight", "desired weight"), col=c("blue", 'green'))
cat()
```
Lets take a moment to look at the outliers
#Notes


Noticed the output: What if I asked to show the general health, weight and weight desired of any of the outliers
```{r}
weightOut <- boxplot.stats(mdata$weight)$out
weightOutRows <- which(mdata$weight %in% c(weightOut))
wtdesireOut <- boxplot.stats(mdata$wtdesire)$out
wtdesireOutRows <- which(mdata$wtdesire %in% c(wtdesireOut))
outRows = unique(union(weightOutRows, wtdesireOutRows))
data = mdata[outRows,c("genhlth","weight","wtdesire")]
summary(data)
```
Lets remove the outliers
```{r}
mdata[outRows,"weight"]=NA
cat( dim(mdata)[1] )
mdata = na.omit(mdata)
cat( dim(mdata)[1] )
```
Plot the new data set can we see more of the detail?
```{r}
plot(mdata$weight, col='blue', pch=19, ylab="weight")
points(mdata$wtdesire, col='green', pch=19)
legend("topleft", 25, pch=c(19, 19), legend=c("actual weight", "desired weight"), col=c("blue", 'green'))
cat()
```
Can we positively say that the variables have a positive association?
#Notes


Let's add a linear regression model and make it red to see better
#Notes

Changing graph appearance by doing several things

More functions to change the appearence of graphs
https://www.w3schools.com/r/r_graph_plot.asp 
Saving Graphs 
#Notes


